Gradual Soundness: Lessons from Static Python

### 2022-01-28 pj-7.1/paper.tex
update

The modelling process helped uncover several critical issues with the
implementation of \SP{}---an important payoff given that \SP{} is running in
production at Instagram.
Overall, we reported 25 bug reports to the \SP{} team via GitHub~(listed in
\cref{a:github-issues}).
Four of these were soundness issues, one of which could be easily exploited to raise
a segmentation fault.
All but one of these soundness bugs have been fixed.
Five issues were relatively minor; these dealt with confusing error messages
and incorrect tests.
The remaining 16 issues report bugs in language design and implementation.
The \SP{} team has acknowledged these bugs as such by applying a specific GitHub label: \lstinline{sp-correctness}.

>>>>

The modelling process helped uncover several critical issues in \SP{}.
This is a very important payoff given that \SP{} is running in production at
Instagram.
Overall, we made 25 bug reports~(\cref{a:github-issues}) to the \SP{} team via GitHub.
Four of these were soundness issues, one of which we could exploit to raise
a segmentation fault.
All but one of these soundness bugs have been fixed.
Of the remaining issues, five were relatively minor; these dealt with confusing error messages
and incorrect tests.
The remaining 16 issues report bugs in language design and implementation.
The \SP{} team has acknowledged these as bugs by applying a specific GitHub label: \lstinline{sp-correctness}.
